---
title: "FARS Coursera Vignette"
author: "MCuddy76"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


library('dplyr')
library('tidyr')
library('readr')
library('maps')
```

This package allows users to load, summarize, and visualize data on fatal motor vehicle accidents from the National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census tracking annual fatal injuries. 

The package includes five functions to read the data, create a file, read the years, summarize the data by year, and to create the visualization at the state level. 

## Reading the data

The first option to loade data is with the fars_read() function. This creates a tibble. 

```{r}
fars_read(filename = filename)
```

## Making the file name
This creates a standard file name for the data. 

```{r}
make_filename(filename=year)
```

## Reading the years
This function will create a vector with a list of monthly data for the given years. This also utilizes the make_filename function and so creates files for each year automatically. 

```{r}
fars_read_years(c(2013:2015))
```

## Summarizing by Year
This creates a summary of all accidents by month for the selected years.

```{r}
fars_summarize_years(c(2013:2015))
```

## Creating the visualization
This plots the frequency of accidents in the selected state(s) for a selected year. Users can select multiple states but only a single year. The maps are drawn using the map() function from the "maps" package. The function takes two arguments. First is the state number, a numeric code for each state. The full list of codes can be found in the function's documentation. The second argument is the year. 

```{r}
fars_map_state(state.num=state.num, year=year)
```





